The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-07 paper/ms.tex
supplementary material

\caption{\label{hrdiagram}
\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
\end{figure*}

>>>>

\caption{\label{hrdiagram}
\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal. An interactive version of this diagram is available as supplementary material from the journal or at \url{benjaminpope.github.io/data/cmd_smear.html}.}
\end{figure*}
